Bow shocks, bow waves, and dust waves

### 2018-06-05 papers/Papers1234/sec-dust-bow-intro.tex
Write long caption for figure 10

\begin{figure}
  \includegraphics[width=\linewidth]{figs/onaxis-stats-plot-MS10-v080-gra002}
  \caption{Vertical cut through Fig.~\ref{fig:decouple-v-n-plane},
    showing bow radius and different regimes for a fixed inflow
    velocity of \SI{80}{km.s^{-1}}.}
  \label{fig:decouple-vertical-cut}
\end{figure}

@@

An example is illustrated in Figure~\ref{fig:decouple-vertical-cut},
where the dust-free bow shock radius is shown by the green dashed line
as a function of stream density, \(n\).  This is calculated for fixed
stream velocity and grain and star properties, so that
\(\tau_* \propto n^{1/2}\) (eq.~[\ref{eq:taustar-typical}]).  In order for
\(R_{\text{dfbs}}\) to match the dust-wave and bow-wave radii at the
point where they cross at \(\tau_* = \tau_{*, \text{max}}\), we find
\(\alpha = 1.5\) is required.  It can be seen that the gas deceleration is
negligible over most of the density range for which a separate dust
wave arises.  Only for \(n > \SI{e3}{cm^{-3}}\) does \(R_{\text{dfbs}}\) begin
to curve up from the general \(n^{-1/2}\) trend, becoming essentially
flat until the full-coupling point at \(n \approx \SI{3e4}{cm^{-3}}\)

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{figs/onaxis-stats-plot-MS10-v080-gra002}
  \caption{Bow radius as a function of stream density for a stream of
    initial velocity \SI{80}{km.s^{-1}}, which interacts with a
    \SI{10}{M_\odot} main-sequence B~star.  This corresponds to a vertical
    slice through the left panel of
    Fig.~\ref{fig:existence-dust-wave}.  At low densities, the
    hydrodynamic bow shock (blue line) is larger than the drag-free
    turnaround radius for small carbon grains, meaning that a grain's
    inertia carries it into the bow shock along with the gas, even
    though the gas--grain coupling is not particularly strong.  At
    densities above about \SI{0.05}{cm^{-3}}, however, this is no
    longer true and a separate dust wave forms outside of the
    hydrodynamic bow shock, which is now dust-free (green dashed
    line).  The grains in the dust wave will occupy a range of radii
    (pale orange shading) between \(\Rmin\) (solid orange line) and
    \(R_\ddag\), the stagnant drift radius.  At densities above about
    \SI{1000}{cm^{-3}}, the gas stream starts to feel the effect of
    passing through the dust wave, and above \SI{3e4}{cm^{-3}}, the
    dust wave and bow shock merge to form a radiative bow wave (red
    line), which becomes an optically thick radiative bow shock
    (purple line) above \SI{e6}{cm^{-3}}.}
  \label{fig:decouple-vertical-cut}
\end{figure}

@@

An example is illustrated in Figure~\ref{fig:decouple-vertical-cut},
where the dust-free bow shock radius is shown by the green dashed line
as a function of stream density, \(n\).  This is calculated for fixed
stream velocity and grain and star properties, so that
\(\tau_* \propto n^{1/2}\) (eq.~[\ref{eq:taustar-typical}]).  In order for
\(R_{\text{dfbs}}\) to match the dust-wave and bow-wave radii at the
point where they cross at \(\tau_* = \tau_{*, \text{max}}\), we find
\(\alpha = 1.5\) is required.  It can be seen that the gas deceleration is
negligible over most of the density range for which a separate dust
wave arises.  Only for \(n > \SI{e3}{cm^{-3}}\) does
\(R_{\text{dfbs}}\) begin to curve up from the general \(n^{-1/2}\)
trend, becoming essentially flat at a value
\(R_{\text{dfbs}} \approx (\kappa/\kappa\grain) R\starstar\) until full-coupling is
established at \(n > \SI{3e4}{cm^{-3}}\).  Note, however, that the
treatment described here is very approximate: it does not take into
account the shock that will form once \(J\drag\) reaches an
appreciable fraction of \(m_{\text{gas}} v_\infty\) and, additionally, it
includes a factor, \(\alpha\), whose appropriate value is unclear.  More
detailed modeling is required to fully understand the bow behavior in
this transition regime.
